Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
adds word 'photons

In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind. 
Unlike \citet{ignace2010}, we consider that UV/X-ray from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
We found that the intrinsic brightness of radio emission from RGHJs are supposedly comparable to canonical hot Jupiters in close-in orbits around main-sequence stars, and $>100$ times brighter than distant Jupiter-twins around main-sequence stars. This implies that they can be searched for 10 times further away, or in 1000 times larger volume. This can compensate the rareness of the evolved stars at least partly. Thus, RGHJs will serve as  reasonable targets for future search for exoplanetary radio emission.

>>>>

In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind. 
Unlike \citet{ignace2010}, we consider that UV/X-ray photons from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
We found that the intrinsic brightness of radio emission from RGHJs are supposedly comparable to canonical hot Jupiters in close-in orbits around main-sequence stars, and $>100$ times brighter than distant Jupiter-twins around main-sequence stars. This implies that they can be searched for 10 times further away, or in 1000 times larger volume. This can compensate the rareness of the evolved stars at least partly. Thus, RGHJs will serve as  reasonable targets for future search for exoplanetary radio emission.
